Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-15 paper/Comparing-belief-in-free-will-and-job-satisfaction-in-the-US-and-Taiwan.qmd
Renaming Folders and Files, added estimand, implemented LLM statement.

---
title: "Comparing belief in free will and job satisfaction in the US and Taiwan "
author: 
  - Ismael Gharbi
  - Zackary Wais
Github Link: "Code and data are available at: https://github.com/zackaryrwais/starter_folder/tree/main."
date: 2024/02/12
date-format: long
abstract: "Free will and job satisfaction are some terminologies that you do not hear often in the same sentence; however go hand in hand with one another. This paper replicates the data compiled from three studies, the first one being in regards to Taiwanese real estate agents, the second study being American online labor workers, and the third study looking into the subject of free will and job satisfaction on an international level. We will also be applying secondary research to aid our understanding of this topic, and how cultural norms affect the responses we receive. As this is an issue that every individual thinks about before entering an industry or accepting a job, we found it to be a topic to be extremely beneficial to us as we are ending our time in university."
format: pdf
output-dir: "./output"

@@

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(knitr)
```

@@

	Free will is a topic that has different meanings depending on the city or country we are in. For us in North America, the idea of free will is more apparent according to a survey concluding that 60% of Americans believe that they have free will (Scientific American 2015). With recent innovations in fields such as psychology, philosophy, and science, the idea of free will has shifted from what the exact term is, to free will’s effects on human beings. This goes to show the neurological connections with free will, specifically that the way we view free will, will later affect a variety of our daily decision-making (Frontiers 2016).
	There are a variety of factors that shift the outcomes of free will, and in this paper, we will take three different studies to help our understanding of free will. The first study we are looking at takes 252 Taiwanese real-estate agents over three months while examining their job satisfaction with free will. The second study takes 137 American workers who are in an online labor market and conducts the same study over six months. The final and largest study takes a sample of 14,062 employees from 16 different countries and examines their country-level moderators. 
	This subject has different meanings in every country, when taking a look at countries outside of North America such as Asia and other Western countries, they have different beliefs of free will on average, specifically that it is not as important as North Americans view it (Frontiers 2017). At its core, free will is to what extent or ability we can our own decisions and have autonomy, as well as the outcomes and consequences of our actions. Studies have shown that when free will is present, the population is happier, more positive, and lives better, contrary to countries that do not have free will (Alquist, Ainsworth, & Baumeister, 2013). Now this idea directly relates to careers, as it is something that individuals spend a majority of their time doing, and would prefer to be happier doing it rather than not being happy. When you have autonomy and free will in your career, you immediately have a higher job satisfaction, as your neurological decision-making is seen in a much clearer manner.

@@

Table 1 : Mean and standard deviation of belief in free will and 
job satisfaction within the Taiwanese real estate agency.
```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

@@

Table 2 : Mean and standard deviation of belief in free will and job
satisfaction within Amazon Mechanical Turk American Workers.
```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_II <- data.frame(
  Job_satisfaction = c(5.29, 1.22),
  Belief_free_will = c(5.28, 0.84)
)

@@

Graph 1 : Bar Chart comparing the belief in free will and job
satisfaction Mehanical Turk American Workers.

```{r}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)

>>>>

---
title: "Comparing belief in free will and job satisfaction in the US and Taiwan "
author: 
  - Ismael Gharbi
  - Zackary Wais
Github Link: "Code and data are available at: https://github.com/zackaryrwais/Comparing-belief-in-free-will-and-job-satisfaction-in-the-US-and-Taiwan/blob/main/paper/references.bib"
date: 2024/02/12
date-format: long
abstract: "Free will and job satisfaction are some terminologies that you do not hear often in the same sentence; however go hand in hand with one another. This paper replicates the data compiled from three studies, the first one being in regards to Taiwanese real estate agents, the second study being American online labor workers, and the third study looking into the subject of free will and job satisfaction on an international level. We will also be applying secondary research to aid our understanding of this topic, and how cultural norms affect the responses we receive. As this is an issue that every individual thinks about before entering an industry or accepting a job, we found it to be a topic to be extremely beneficial to us as we are ending our time in university."
format: pdf
output-dir: "./output"
bibliography: references.bib

@@

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(knitr)
library(dplyr)
```

@@

	Free will is a topic that has different meanings depending on the city or country we are in. For us in North America, the idea of free will is more apparent according to a survey concluding that 60% of Americans believe that they have free will (Scientific American 2015). With recent innovations in fields such as psychology, philosophy, and science, the idea of free will has shifted from what the exact term is, to free will’s effects on human beings. This goes to show the neurological connections with free will, specifically that the way we view free will, will later affect a variety of our daily decision-making (Frontiers 2016).
	There are a variety of factors that shift the outcomes of free will, and in this paper, we will take three different studies to help our understanding of free will. The first study we are looking at takes 252 Taiwanese real-estate agents over three months while examining their job satisfaction with free will. The second study takes 137 American workers who are in an online labor market and conducts the same study over six months. The estimand here for the belief in free will would be the The Rakos et al and the full scale for the second study, as for the Job satisfaction it is the adaptation of the five
items short scale of Brayfield and Rothe (1951) constructed by Judge, Locke, Durham, and Kluger (1998). Those scales are shown here from 0 to 10 for the sake of simplicity.

	This subject has different meanings in every country, when taking a look at countries outside of North America such as Asia and other Western countries, they have different beliefs of free will on average, specifically that it is not as important as North Americans view it (Frontiers 2017). At its core, free will is to what extent or ability we can our own decisions and have autonomy, as well as the outcomes and consequences of our actions. Studies have shown that when free will is present, the population is happier, more positive, and lives better, contrary to countries that do not have free will (Alquist, Ainsworth, & Baumeister, 2013). Now this idea directly relates to careers, as it is something that individuals spend a majority of their time doing, and would prefer to be happier doing it rather than not being happy. When you have autonomy and free will in your career, you immediately have a higher job satisfaction, as your neurological decision-making is seen in a much clearer manner.

@@

Table 1 : Mean and standard deviation of belief in free will and 
job satisfaction within the Taiwanese real estate agency.
```{r, hide_code=TRUE}

Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

@@

Table 2 : Mean and standard deviation of belief in free will and job
satisfaction within Amazon Mechanical Turk American Workers.
```{r, hide_code=TRUE}

Table_II <- data.frame(
  Job_satisfaction = c(5.29, 1.22),
  Belief_free_will = c(5.28, 0.84)
)

@@

Graph 1 below with a y-axis depicting the US and Taiwan at Time 1 and 2 and a 
x-axis depicting a scale from 0 to 10. Both country has two bars measured on 
the scale depicting the belief in Free Will and the job satisfaction. We can 
observe that the average american worker has a higher belief in Free Will (5.28)
compared to his Taiwanese counterpart (3.99) but a relatively smaller job
satisfaction (5.64 and 5.74 compared to 5.29 in the US). This may suggest a low 
negative to no correlation between belief in Free Will and Job Satisfaction due
to the different circumstances of the samples.

Graph 1 : Bar Chart comparing the average belief in free will and job
satisfaction between MTurk American Workers and employees in Taiwan.

```{r, hide_code=TRUE}

library(ggplot2)
library(dplyr)
